\chapter*{Acknowledgments}

Working as a PhD student in Eurecom was a great experience that would not be achieved without the help and support of many people, who I would like to acknowledge here.    
\\
\\
First and foremost, I would like to thank my supervisor Dr. Rapha\"el Troncy for his invaluable support and great guidance throughout my study. I would like to express my gratitude to him for provided me with a lot of freedom to pursue my research. This work would not have been possible without his scientific knowledge and constructive advice.
\\
\\
I would like to extend my sincere thanks to my committee members, the reviewers Prof. Geert-Jan Houben and Dr. Catherine Faron-Zucker, and the examiners Prof. Talel Abdessalem, Prof. John Domingue and Dr. Tommaso Di Noia for their precious time and shared insights.
\\
\\
I am particularly indebted to my colleagues who more or less directly contributed to my Ph.D. Precisely, I would like to acknowledge the support of my friends: Vuk, Ghislain, Jos\'e Luis and Giuseppe for their inspiring collaboration and fruitful discussions. It was a pleasure to work and exchange with them. Also, I thank all those working at EURECOM, they made my stay very pleasant.
\\
\\
I owe my deepest gratitude to my parents, Nejiba and Abdessalem, my sisters Sonia and Hela and my brother Ahmed for their unwavering encouragement, devotion and love.  Last but not least, special thanks go to my friends for their constant friendship, moral and infinite support.
